MLH1 data report 

### 2017-12-07 rmd_report.rmd
catching up on updates

MLH1_data <- MLH1_data %>%
  arrange(category) %>%
  mutate(Original.Name = factor(Original.Name)) #another category that you want the order to match
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(category),])

>>>>

MLH1_data <- MLH1_data %>%
  arrange(category) %>%
  mutate(Original.Name = factor(Original.Name)) #another category that you want the order to match

MLH1_data <- with(MLH1_data, MLH1_data[order(category),])
